Enhancement of SDR in Thessaloniki

### 2024-06-06 GHI_enh_06_sza.tex
Commit 2024-06-06 20:17

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_06_sza_files/figure-latex/sza-1} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_06_sza_files/figure-latex/sza-2} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_06_sza_files/figure-latex/sza-3} \end{center}

@@

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_06_sza_files/figure-latex/sza_month-1} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_06_sza_files/figure-latex/sza_month-2} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_06_sza_files/figure-latex/sza_month-3} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_06_sza_files/figure-latex/sza_month-4} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_06_sza_files/figure-latex/sza_month-5} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_06_sza_files/figure-latex/sza_month-6} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_06_sza_files/figure-latex/sza_month-7} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_06_sza_files/figure-latex/sza_month-8} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_06_sza_files/figure-latex/sza_month-9} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_06_sza_files/figure-latex/sza_month-10} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_06_sza_files/figure-latex/sza_month-11} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_06_sza_files/figure-latex/sza_month-12} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_06_sza_files/figure-latex/sza_month-13} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_06_sza_files/figure-latex/sza_month-14} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_06_sza_files/figure-latex/sza_month-15} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_06_sza_files/figure-latex/sza_month-16} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_06_sza_files/figure-latex/sza_month-17} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_06_sza_files/figure-latex/sza_month-18} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_06_sza_files/figure-latex/sza_month-19} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_06_sza_files/figure-latex/sza_month-20} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_06_sza_files/figure-latex/sza_month-21} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_06_sza_files/figure-latex/sza_month-22} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_06_sza_files/figure-latex/sza_month-23} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_06_sza_files/figure-latex/sza_month-24} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_06_sza_files/figure-latex/sza_month-25} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_06_sza_files/figure-latex/sza_month-26} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_06_sza_files/figure-latex/sza_month-27} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_06_sza_files/figure-latex/sza_month-28} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_06_sza_files/figure-latex/sza_month-29} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_06_sza_files/figure-latex/sza_month-30} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_06_sza_files/figure-latex/sza_month-31} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_06_sza_files/figure-latex/sza_month-32} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_06_sza_files/figure-latex/sza_month-33} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_06_sza_files/figure-latex/sza_month-34} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_06_sza_files/figure-latex/sza_month-35} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_06_sza_files/figure-latex/sza_month-36} \end{center}

@@

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_06_sza_files/figure-latex/sza_doy-1} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_06_sza_files/figure-latex/sza_doy-2} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_06_sza_files/figure-latex/sza_doy-3} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_06_sza_files/figure-latex/sza_doy-4} \end{center}

@@

\begin{verbatim}
2024-04-14 00:55:04.2 athan@tyler GHI_enh_06_sza.R 0.288979 mins
\end{verbatim}

>>>>

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_06_sza_files/figure-latex/sza-1}

}

\caption{ - empty caption - }\label{fig:sza-1}
\end{figure}
\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_06_sza_files/figure-latex/sza-2}

}

\caption{ - empty caption - }\label{fig:sza-2}
\end{figure}
\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_06_sza_files/figure-latex/sza-3}

}

\caption{ - empty caption - }\label{fig:sza-3}
\end{figure}

@@

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_06_sza_files/figure-latex/sza-month-1}

}

\caption{ - empty caption - }\label{fig:sza-month-1}
\end{figure}
\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_06_sza_files/figure-latex/sza-month-2}

}

\caption{ - empty caption - }\label{fig:sza-month-2}
\end{figure}
\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_06_sza_files/figure-latex/sza-month-3}

}

\caption{ - empty caption - }\label{fig:sza-month-3}
\end{figure}
\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_06_sza_files/figure-latex/sza-month-4}

}

\caption{ - empty caption - }\label{fig:sza-month-4}
\end{figure}
\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_06_sza_files/figure-latex/sza-month-5}

}

\caption{ - empty caption - }\label{fig:sza-month-5}
\end{figure}
\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_06_sza_files/figure-latex/sza-month-6}

}

\caption{ - empty caption - }\label{fig:sza-month-6}
\end{figure}
\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_06_sza_files/figure-latex/sza-month-7}

}

\caption{ - empty caption - }\label{fig:sza-month-7}
\end{figure}
\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_06_sza_files/figure-latex/sza-month-8}

}

\caption{ - empty caption - }\label{fig:sza-month-8}
\end{figure}
\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_06_sza_files/figure-latex/sza-month-9}

}

\caption{ - empty caption - }\label{fig:sza-month-9}
\end{figure}
\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_06_sza_files/figure-latex/sza-month-10}

}

\caption{ - empty caption - }\label{fig:sza-month-10}
\end{figure}
\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_06_sza_files/figure-latex/sza-month-11}

}

\caption{ - empty caption - }\label{fig:sza-month-11}
\end{figure}
\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_06_sza_files/figure-latex/sza-month-12}

}

\caption{ - empty caption - }\label{fig:sza-month-12}
\end{figure}
\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_06_sza_files/figure-latex/sza-month-13}

}

\caption{ - empty caption - }\label{fig:sza-month-13}
\end{figure}
\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_06_sza_files/figure-latex/sza-month-14}

}

\caption{ - empty caption - }\label{fig:sza-month-14}
\end{figure}
\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_06_sza_files/figure-latex/sza-month-15}

}

\caption{ - empty caption - }\label{fig:sza-month-15}
\end{figure}
\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_06_sza_files/figure-latex/sza-month-16}

}

\caption{ - empty caption - }\label{fig:sza-month-16}
\end{figure}
\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_06_sza_files/figure-latex/sza-month-17}

}

\caption{ - empty caption - }\label{fig:sza-month-17}
\end{figure}
\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_06_sza_files/figure-latex/sza-month-18}

}

\caption{ - empty caption - }\label{fig:sza-month-18}
\end{figure}
\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_06_sza_files/figure-latex/sza-month-19}

}

\caption{ - empty caption - }\label{fig:sza-month-19}
\end{figure}
\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_06_sza_files/figure-latex/sza-month-20}

}

\caption{ - empty caption - }\label{fig:sza-month-20}
\end{figure}
\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_06_sza_files/figure-latex/sza-month-21}

}

\caption{ - empty caption - }\label{fig:sza-month-21}
\end{figure}
\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_06_sza_files/figure-latex/sza-month-22}

}

\caption{ - empty caption - }\label{fig:sza-month-22}
\end{figure}
\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_06_sza_files/figure-latex/sza-month-23}

}

\caption{ - empty caption - }\label{fig:sza-month-23}
\end{figure}
\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_06_sza_files/figure-latex/sza-month-24}

}

\caption{ - empty caption - }\label{fig:sza-month-24}
\end{figure}
\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_06_sza_files/figure-latex/sza-month-25}

}

\caption{ - empty caption - }\label{fig:sza-month-25}
\end{figure}
\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_06_sza_files/figure-latex/sza-month-26}

}

\caption{ - empty caption - }\label{fig:sza-month-26}
\end{figure}
\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_06_sza_files/figure-latex/sza-month-27}

}

\caption{ - empty caption - }\label{fig:sza-month-27}
\end{figure}
\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_06_sza_files/figure-latex/sza-month-28}

}

\caption{ - empty caption - }\label{fig:sza-month-28}
\end{figure}
\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_06_sza_files/figure-latex/sza-month-29}

}

\caption{ - empty caption - }\label{fig:sza-month-29}
\end{figure}
\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_06_sza_files/figure-latex/sza-month-30}

}

\caption{ - empty caption - }\label{fig:sza-month-30}
\end{figure}
\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_06_sza_files/figure-latex/sza-month-31}

}

\caption{ - empty caption - }\label{fig:sza-month-31}
\end{figure}
\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_06_sza_files/figure-latex/sza-month-32}

}

\caption{ - empty caption - }\label{fig:sza-month-32}
\end{figure}
\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_06_sza_files/figure-latex/sza-month-33}

}

\caption{ - empty caption - }\label{fig:sza-month-33}
\end{figure}
\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_06_sza_files/figure-latex/sza-month-34}

}

\caption{ - empty caption - }\label{fig:sza-month-34}
\end{figure}
\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_06_sza_files/figure-latex/sza-month-35}

}

\caption{ - empty caption - }\label{fig:sza-month-35}
\end{figure}
\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_06_sza_files/figure-latex/sza-month-36}

}

\caption{ - empty caption - }\label{fig:sza-month-36}
\end{figure}

@@

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_06_sza_files/figure-latex/sza-doy-1}

}

\caption{ - empty caption - }\label{fig:sza-doy-1}
\end{figure}
\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_06_sza_files/figure-latex/sza-doy-2}

}

\caption{ - empty caption - }\label{fig:sza-doy-2}
\end{figure}
\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_06_sza_files/figure-latex/sza-doy-3}

}

\caption{ - empty caption - }\label{fig:sza-doy-3}
\end{figure}
\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_06_sza_files/figure-latex/sza-doy-4}

}

\caption{ - empty caption - }\label{fig:sza-doy-4}
\end{figure}

@@

\begin{verbatim}
2024-06-06 15:04:39.7 athan@tyler GHI_enh_06_sza.R 0.661558 mins
\end{verbatim}
